Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-10-07 paper/paper.Rmd
add model colours to figure legends

```{r vis-forecasts, fig.cap = "a.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one and four weeks). 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time. b.) A replicate of a.) but with incidence rates on the log scale. c.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom on the log scale.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_forecast_custom(forecasts, log = FALSE) |
  plot_forecast_custom(forecasts, log = TRUE) +
  labs(y = "") |
  plot_wis(wis, locs)
) +
  plot_layout(widths = c(2, 2, 1), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre", axis.title = element_text(size = 16)
  )
suppressWarnings(print(p))
```

@@

Evaluating the ensemble and surrogate models using the WIS across all locations and forecast dates we found that the mean relative performance of the surrogate model was `r relative_wis_by_horizon[horizon == 1, ris]` at the one-week horizon, `r relative_wis_by_horizon[horizon == 2, ris]` at the two-week horizon, `r relative_wis_by_horizon[horizon == 3, ris]` at the three-week horizon, and `r relative_wis_by_horizon[horizon == 4, ris]` at the four-week horizon, indicating that the ensemble forecast outperformed the surrogate forecast for all horizons by at least 25% and that the relative performance of the surrogate model degraded as the forecast horizon increased  (Figure \@ref(fig:assemble-eval) c).
Much of this outperformance, especially at longer forecast horizons, was driven by a relatively small subset of forecasts with relative performance having a heavy tail (Figure \@ref(fig:assemble-eval) a). 
If we instead consider median relative performance (note this is not a proper scoring rule) we find that, relative to the ensemble, the surrogate scored `r relative_median_wis_by_horizon[horizon == 1, ris]` at the one week horizon, `r relative_median_wis_by_horizon[horizon == 2, ris]` at the two week horizon, `r relative_median_wis_by_horizon[horizon == 3, ris]` at the three week horizon, and `r relative_median_wis_by_horizon[horizon == 4, ris]` at the four week horizon.
This would suggest that an increasingly skewed score distribution as the forecast horizon increased is responsible for the increase in the mean relative score (Figure \@ref(fig:assemble-eval) a).
`r relative_wis_thresholds[, better_than]` of individual surrogate forecasts scored better than the comparable ensemble forecast, `r relative_wis_thresholds[, fifty_percent]` performed within 50% of the comparable ensemble forecast, and `r relative_wis_thresholds[, more_than_100_percent]` had a more than 100% worse WIS than the comparable ensemble forecast.

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%", fig.cap = "a.) Empirical coverage of the surrogate and ensemble forecasts at the 90\\%, 60\\%, and 30\\% prediction intervals stratified by forecast horizon. Ideally, a well-calibrated forecast should have empirical coverage for a given prediction interval that equals the nominal level of the interval (i.e., 30\\%, 60\\% and 90\\%, respectively). b.) Empirical coverage by quantile for both the surrogate and ensemble forecasts. A well-calibrated forecast should have empirical quantiles that match the theoretical ones. The green area of this figure corresponds to conservative forecasts. c.) Median relative weighted interval score by quantile and forecast horizon for the surrogate forecast compared to the ensemble forecast. d.) Bias of the ensemble and surrogate forecasts stratified by horizon."}
p <- (
  (
    (
      plot_coverage_range(coverage, ranges)
    )
  ) | (
    plot_coverage_quantiles(scores) + (
      plot_rel_score_by_quantile(relative_interval_score) +
      plot_bias(summary_performance)
    ) +
    plot_layout(heights = c(2, 1), guides = "collect")
  )
) +
  plot_layout(widths = c(1, 2), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre", axis.title = element_text(size = 16)
  )
suppressWarnings(print(p))
```

>>>>

```{r vis-forecasts, fig.cap = "a.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom, by forecast horizon (one and four weeks) for the surrogate model (orange) and forecast ensemble (green). 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time. b.) A replicate of a.) but with incidence rates on the log scale. c.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom on the log scale.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_forecast_custom(forecasts, log = FALSE) |
  plot_forecast_custom(forecasts, log = TRUE) +
  labs(y = "") |
  plot_wis(wis, locs)
) +
  plot_layout(widths = c(2, 2, 1), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre", axis.title = element_text(size = 16)
  )
suppressWarnings(print(p))
```

@@

Evaluating the ensemble and surrogate models using the WIS across all locations and forecast dates we found that the mean relative performance of the surrogate model was `r relative_wis_by_horizon[horizon == 1, ris]` at the one-week horizon, `r relative_wis_by_horizon[horizon == 2, ris]` at the two-week horizon, `r relative_wis_by_horizon[horizon == 3, ris]` at the three-week horizon, and `r relative_wis_by_horizon[horizon == 4, ris]` at the four-week horizon, indicating that the ensemble forecast outperformed the surrogate forecast for all horizons by at least 25% and that the relative performance of the surrogate model degraded as the forecast horizon increased  (Figure \@ref(fig:assemble-eval) c).
Much of this outperformance, especially at longer forecast horizons, was driven by a small subset of forecasts with relative performance having a heavy tail (Figure \@ref(fig:assemble-eval) a). 
If we instead consider median relative performance (note this is not a proper scoring rule and should not be used to choose between models) we find that, relative to the ensemble, the surrogate scored `r relative_median_wis_by_horizon[horizon == 1, ris]` at the one week horizon, `r relative_median_wis_by_horizon[horizon == 2, ris]` at the two week horizon, `r relative_median_wis_by_horizon[horizon == 3, ris]` at the three week horizon, and `r relative_median_wis_by_horizon[horizon == 4, ris]` at the four week horizon.
This would suggest that an increasingly skewed score distribution as the forecast horizon increased is responsible for the increase in the mean relative score (Figure \@ref(fig:assemble-eval) a).
`r relative_wis_thresholds[, better_than]` of individual surrogate forecasts scored better than the comparable ensemble forecast, `r relative_wis_thresholds[, fifty_percent]` performed within 50% of the comparable ensemble forecast, and `r relative_wis_thresholds[, more_than_100_percent]` had a more than 100% worse WIS than the comparable ensemble forecast.

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%", fig.cap = "a.) Empirical coverage of the surrogate (orange) and ensemble (green) forecasts at the 90\\%, 60\\%, and 30\\% prediction intervals stratified by forecast horizon. Ideally, a well-calibrated forecast should have empirical coverage for a given prediction interval that equals the nominal level of the interval (i.e., 30\\%, 60\\% and 90\\%, respectively). b.) Empirical coverage by quantile for both the surrogate and ensemble forecasts. A well-calibrated forecast should have empirical quantiles that match the theoretical ones. The green area of this figure corresponds to conservative forecasts. c.) Median relative weighted interval score by quantile and forecast horizon for the surrogate forecast compared to the ensemble forecast. d.) Bias of the ensemble and surrogate forecasts stratified by horizon."}
p <- (
  (
    (
      plot_coverage_range(coverage, ranges)
    )
  ) | (
    plot_coverage_quantiles(scores) + (
      plot_rel_score_by_quantile(relative_interval_score) +
      plot_bias(summary_performance)
    ) +
    plot_layout(heights = c(2, 1), guides = "collect")
  )
) +
  plot_layout(widths = c(1, 2), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre", axis.title = element_text(size = 16)
  )
suppressWarnings(print(p))
```
